---
output:
  github_document:
    html_preview: false

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Paws, an AWS SDK for R

[![Build Status](https://travis-ci.com/paws-r/paws.svg?branch=master)](https://travis-ci.com/paws-r/paws)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/2ma1spb2f55129qc/branch/master?svg=true)](https://ci.appveyor.com/project/paws-r/paws/branch/master)
[![codecov](https://codecov.io/gh/paws-r/paws/branch/master/graph/badge.svg)](https://codecov.io/gh/paws-r/paws)


Paws is a **P**ackage for **A**mazon **W**eb **S**ervices. Paws provides
access to the full suite of AWS services from within R.

Each AWS service has its own R package within Paws. For example, to use EC2, use
the `paws.ec2` package.

**Disclaimer**: Paws is not a product of or supported by Amazon Web Services.

Paws is based on the design and implementation of the 
[AWS SDK for Go](https://github.com/aws/aws-sdk-go) and it uses AWS's API 
definition files and API documentation from the 
[AWS SDK for JavaScript](https://github.com/aws/aws-sdk-js).


## Getting Started

### Installation

Paws is currently available on GitHub. See [the list of available packages
here](service). Install a package (e.g. `paws.ec2`) using:

```{r, eval = FALSE}
devtools::install_github("paws-r/paws/service/paws.ec2")
```

### Credentials

First, set up your credentials and region. Here we set them within R. Paws also
supports OS envrionment variables, AWS credential files, and IAM roles. See 
[docs/credentials.md](docs/credentials.md) for more info.

```{r, eval = FALSE}
Sys.setenv(
  AWS_ACCESS_KEY_ID = "abc",
  AWS_SECRET_ACCESS_KEY = "123",
  AWS_REGION = "us-east-1"
)
```

### Run an operation

Here we launch an EC2 instance using the `run_instances` function. See the
[examples](examples) folder for more examples.

```{r, eval = FALSE}
ec2 <- paws.ec2::run_instances(
  ImageId = "ami-f973ab84",
  InstanceType = "t2.micro",
  KeyName = "default",
  MinCount = 1,
  MaxCount = 1,
  TagSpecifications = list(
    list(
      ResourceType = "instance",
      Tags = list(
        list(Key = "webserver", Value = "production"))
    )
  )
)
```

We can get a list of all of our instances with `describe_instances`.

```{r, eval = FALSE}
paws.ec2::describe_instances()
```

Using AWS services can cost money, so remember to shut down anything you start.

```{r, eval = FALSE}
paws.ec2::terminate_instances(
  InstanceIds = ec2$Instances[[1]]$InstanceId
)
```

### Documentation

You can see all the operations for a given service, like EC2, by looking through
the package documentation.

```{r, eval = FALSE}
help(package = "paws.ec2")
```

We also have examples for [EC2](examples/ec2.R), [S3](examples/s3.R), 
[SQS](examples/sqs.R), [SNS](examples/sns.R), [DynamoDB](examples/dynamodb.R),
[Lambda](examples/lambda.R), [Batch](examples/batch.R), and
[Comprehend](examples/comprehend.R).
